<!DOCTYPE html>
<html>
  <head>
    <!-- htmlwidgets dependencies --> 
    
    
    

    

    <title>Data science jobs in the non-profit sector – Erin Grand – Interested in data science and education</title>

        <meta charset="utf-8" />
    <meta content='text/html; charset=utf-8' http-equiv='Content-Type'>
    <meta http-equiv='X-UA-Compatible' content='IE=edge'>
    <meta name='viewport' content='width=device-width, initial-scale=1.0, maximum-scale=1.0'>

    
    <meta name="description" content="Interested in data science and education">
    <meta property="og:description" content="Interested in data science and education" />
    
    <meta name="author" content="Erin Grand" />

    
    <meta property="og:title" content="Data science jobs in the non-profit sector" />
    <meta property="twitter:title" content="Data science jobs in the non-profit sector" />
    

    <!--[if lt IE 9]>
      <script src="http://html5shiv.googlecode.com/svn/trunk/html5.js"></script>
    <![endif]-->

    <link rel="stylesheet" type="text/css" href="/style.css" />
    <link rel="alternate" type="application/rss+xml" title="Erin Grand - Interested in data science and education" href="/feed.xml" />

    <!-- Created with Jekyll Now - http://github.com/barryclark/jekyll-now -->
  </head>

  <body>
    <div class="wrapper-masthead">
      <div class="container">
        <header class="masthead clearfix">
          <a href="/" class="site-avatar"><img src="https://avatars.githubusercontent.com/u/6360871?v=3" /></a>

          <div class="site-info">
            <h1 class="site-name"><a href="/">Erin Grand</a></h1>
            <p class="site-description">Interested in data science and education</p>
          </div>

          <nav>
            <a href="/">Blog</a>
            <a href="/about">About</a>
            <a href="/projects">Projects</a>
            <a href="/archive">Archive</a>
          </nav>
        </header>
      </div>
    </div>

    <div id="main" role="main" class="container">
      

<article class="post">
<h1>Data science jobs in the non-profit sector</h1>


<div>
<ul class="tag_list_in_post">
<emph> Tags: </emph>

 <a class="tag_list_link" href="/tag/data science jobs non-profit">data science jobs non-profit</a>

</ul>
</div>




<p id="post-meta"></p>

  <div class="entry">
    ```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(googlesheets4)
library(janitor)
```


```{r}
doc <- gs_title("Songs played")
```

```{r}
gs_read(doc, 1, verbose = FALSE) %>%
  clean_names() %>%
  mutate(date = str_replace(date, " at ", " "),
         date = lubridate::mdy_hm(date),
         weekday = lubridate::wday(date, label = TRUE, abbr = FALSE),
         hour = lubridate::hour(date),
         explicit = str_detect(album, "Explicit"),
         next_date = lead(date),
         time_diff = as.numeric(next_date - date, units = "mins"),
         time_diff = if_else(time_diff <= 10, time_diff, NA_real_)) %>%
  filter(time_diff > 1 | is.na(time_diff)) # skipped songs
```


  </div>

  <div class="date">
    Written on 
  </div>

  
<div class="comments">
	<div id="disqus_thread"></div>
	<script type="text/javascript">
    
	    var disqus_shortname = 'astroeringrand'; 

	    (function() {
	        var dsq = document.createElement('script'); dsq.type = 'text/javascript'; dsq.async = true;
	        dsq.src = '//' + disqus_shortname + '.disqus.com/embed.js';
	        (document.getElementsByTagName('head')[0] || document.getElementsByTagName('body')[0]).appendChild(dsq);
	    })();

	</script>
	<noscript>Please enable JavaScript to view the <a href="http://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>
</div>

</article>

    </div>

    <div class="wrapper-footer">
      <div class="container">
        <footer class="footer">
          
<a href="mailto:eringrand@gmail.com"><i class="svg-icon email"></i></a>


<a href="https://github.com/eringrand"><i class="svg-icon github"></i></a>
<a href="https://instagram.com/astroeringrand"><i class="svg-icon instagram"></i></a>
<a href="https://www.linkedin.com/in/eringrand"><i class="svg-icon linkedin"></i></a>

<a href="/feed.xml"><i class="svg-icon rss"></i></a>
<a href="https://www.twitter.com/astroeringrand"><i class="svg-icon twitter"></i></a>

<a href="https://youtube.com/channel/UCAMkBTcL3PAjgnETfWWKkCQ"><i class="svg-icon youtube"></i></a>

        </footer>
      </div>
    </div>

    
	<!-- Google Analytics -->
	<script>
		(function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
		(i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
		m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
		})(window,document,'script','//www.google-analytics.com/analytics.js','ga');
		
		ga('create', 'UA-59780775-1', 'auto');
		ga('send', 'pageview', {
		  'page': '/Rmds/2018-5-01-amazonmusic.Rmd',
		  'title': 'Data science jobs in the non-profit sector'
		});
	</script>
	<!-- End Google Analytics -->


  </body>
</html>



