<!DOCTYPE html>
<html>
  <head>
    <!-- htmlwidgets dependencies --> 
    
    
    

    

    <title>Reviewing my old live journal posts – Erin Grand – Interested in data science and education</title>

        <meta charset="utf-8" />
    <meta content='text/html; charset=utf-8' http-equiv='Content-Type'>
    <meta http-equiv='X-UA-Compatible' content='IE=edge'>
    <meta name='viewport' content='width=device-width, initial-scale=1.0, maximum-scale=1.0'>

    
    <meta name="description" content="Interested in data science and education">
    <meta property="og:description" content="Interested in data science and education" />
    
    <meta name="author" content="Erin Grand" />

    
    <meta property="og:title" content="Reviewing my old live journal posts" />
    <meta property="twitter:title" content="Reviewing my old live journal posts" />
    

    <!--[if lt IE 9]>
      <script src="http://html5shiv.googlecode.com/svn/trunk/html5.js"></script>
    <![endif]-->

    <link rel="stylesheet" type="text/css" href="/style.css" />
    <link rel="alternate" type="application/rss+xml" title="Erin Grand - Interested in data science and education" href="/feed.xml" />

    <!-- Created with Jekyll Now - http://github.com/barryclark/jekyll-now -->
  </head>

  <body>
    <div class="wrapper-masthead">
      <div class="container">
        <header class="masthead clearfix">
          <a href="/" class="site-avatar"><img src="https://avatars.githubusercontent.com/u/6360871?v=3" /></a>

          <div class="site-info">
            <h1 class="site-name"><a href="/">Erin Grand</a></h1>
            <p class="site-description">Interested in data science and education</p>
          </div>

          <nav>
            <a href="/">Blog</a>
            <a href="/about">About</a>
            <a href="/projects">Projects</a>
            <a href="/archive">Archive</a>
          </nav>
        </header>
      </div>
    </div>

    <div id="main" role="main" class="container">
      

<article class="post">
<h1>Reviewing my old live journal posts</h1>


<div>
<ul class="tag_list_in_post">
<emph> Tags: </emph>

 <a class="tag_list_link" href="/tag/data">data</a>

</ul>
</div>




<p id="post-meta"></p>

  <div class="entry">
    ```{r message=TRUE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(tidyverse)
library(lubridate)
library(tidytext)
library(hunspell)
library(ggrepel)
library(cowplot)
```

I'm about to BARE MY SOUL to the internet. Well, the soul of my teenage self... Get ready!

I downloaded all my past Live Journal entities to a folder on my desktop in the same CSV format, so that I could easily load them in for analysis. I am pleasantly surprised that Live Journal made it so easy to download my history like this! I did have to click the same button a ton of time - but I did get all my data.

```{r echo = FALSE}
lj_files <- list.files("~/github/LJ/", pattern = "stumpthegreat", full.names = TRUE)

lj_df <- map_dfr(lj_files, read_csv, col_types = cols(
  itemid = col_character(),
  eventtime = col_character(),
  logtime = col_character(),
  subject = col_character(),
  event = col_character(),
  security = col_character(),
  allowmask = col_character(),
  current_music = col_character(),
  current_mood = col_character() )
) %>%
  distinct()
```

The next step was to take every journal and separate out the individual words using '[tidytext](https://cran.r-project.org/web/packages/tidytext/vignettes/tidytext.html).'

```{r}
lj_words <- lj_df %>%
  select(itemid, eventtime, logtime, subject, current_music, current_mood, event) %>%
  mutate(across(c(eventtime, logtime), ymd_hms),
         year = year(logtime),
         month = month(logtime),
         ) %>%
  mutate(event = str_remove_all(event, "'")) %>%
  unnest_tokens(word, event, token = "words", format = "html", strip_url = FALSE) 
```

Not included in this blog post, for privacy of my teenage friends, I also cleaned and changed names of my friends and locations to clean the data and protect their privacy. For example, instead of the name "Linda" you may see "nameofsister". 

```{r include=FALSE, echo = FALSE}
change_names_df <- tibble::tribble(
                                ~word, ~new_name,
                         "melissa",      "bestfriend",
                        "danielle",      "otherbestfriend",
                           "jason",      "hsboyfriend",
                            "jeff",      "gaybestfriend",
                            "mara",      "campfriend",
                            "tara",      "friend",
                           "laura",      "sisterfriend",
                           "kevin",      "neighbor",
                            "kyle",      "bestfriendboyfriend",
                             "sam",      "collegefriend",
                 "flyingarmadillo",      "bestfriend",
                 "firefaerie", "blogofpersonIdontremeber",
                             "meg",      "stillbestfriend",
                         "megkips",      "stillbestfriend",
                        "kykenobi",      "bestfriendboyfriend",
                          "hayley",      "cousin",
                             "mia",      "othercampfriend",
                           "marla",      "jewfriend",
                             "jon",      "secondexbf",
                           "linda",      "sister",
                           "alex",      "firstexbf"
                 ) %>%
  filter(! is.na(new_name)) %>%
  mutate(new_name = str_c("nameof", new_name))

lj_words_protect <- lj_words %>%
  left_join(change_names_df) %>%
  mutate(word = coalesce(new_name, word)) %>%
  select(-new_name)

my_stop_words_list <- c("loki", "german", "norse", "odin", 
                        "firefaerie",
                        "bon", "jovi", 
                        "jeff", "mara", "tara", "laura",
                        "jess", "kevin", "kyle", "sam", 
                        "alice",
                        "gaiman", "boro",
                        "abbie",
                        "flyingarmadillo", "meg", "megkips", "kykenobi", "hayley",
                        "neopets", "stumpthegreat", "thisangelinhell", 
                        "zarephathcs",
                        "photobucket", "lotr",
                        "acdc", "alg", "x", "v",
                        pull(change_names_df, word),
                        pull(change_names_df, new_name),
                        "&aelig;sir", "photobucket", "quizzical") %>% 
                      unique()

my_stop_words <- tibble(word = my_stop_words_list, lexicon = "Me") %>%
  bind_rows(stop_words)
```

I was (and continue to be) terrible at spelling words correctly and also terrible at checking what I've typed after the fact. I use 'hunspell' here in an attempt to fix some of the most common issues. Does this spell check get everything? No! But alas, I am a terrible speller and we move on in life.

```{r}
lj_words_spell_check <- lj_words_protect %>%
  anti_join(my_stop_words, by = "word") %>%
  count(word) %>%
  rowwise() %>%
  mutate(spell_check = hunspell(word)) %>%
  filter(length(spell_check) >= 1) %>%
  mutate(suggest = hunspell_suggest(spell_check)) 
```

```{r echo = FALSE}
correct_spell_check <- tibble::tribble(
          ~word,   ~suggest_pick,
        "acess",     "access",
        "forte",     "forget",
     "abosulty", "absolutely",
     "absoltly", "absolutely",
      "adtally",   "actually",
       "akward",    "awkward",
         "dont",      "don't",
          "don",      "don't",
         "aint",      "ain't",
           "im",        "i'm",
         "boro",  "hillsborough",
     "dint", "didn't",
     "u", "you"
     )
```

```{r}
lj_correct <- lj_words_spell_check %>%
  filter(length(suggest) > 0) %>%
  mutate(suggest_pick = pluck(suggest, 1)) %>% # just pick the first one because I am lazy
  ungroup() %>%
  unnest(suggest_pick) %>%
  select(word, suggest_pick) 
```

```{r echo = FALSE}
lj_correct <- lj_correct %>%
  anti_join(correct_spell_check, by = "word") %>%
  bind_rows(correct_spell_check)
```

```{r}
lj_words_corrected <- lj_words_protect %>%
  left_join(lj_correct, by = "word") %>%
  mutate(word = coalesce(suggest_pick, word)) %>%
  unnest_tokens(output = "word", input = word) # used because sometimes the correction is actually 2+ words now 
```

## Now we move on to actaul analysis!
The data is clean, or at least as clean as it is going to get today.

### Word counts

I start with TF-IDF. The goal here is to see what I was talking about each year and how it may differ as I got older. As a reminder, I have changed the names of all my friends and family for privacy. That way you don't know who "nameofbestfriend" is and why I stopped mentioning "nameofbestfriend" in 2006. (We had a bit of a falling out at the end of HS.)

```{r}
tfidf <- lj_words_corrected %>%
  count(year, word) %>% 
  tidytext::bind_tf_idf(word, year, n) %>%
  anti_join(stop_words, by = "word") %>%
  group_by(year) %>%
  top_n(n = 10, wt = tf_idf) %>%
  ungroup() %>%
  filter(n >= 2) 
```

```{r echo = FALSE}
tfidf %>%
  ggplot(aes(x = tf_idf, y = reorder_within(word, by = tf_idf, within = year), 
             fill = factor(year)) ) +
  geom_col() +
  scale_y_reordered() +
  guides(fill = FALSE) +
  viridis::scale_fill_viridis(discrete = TRUE, end = 0.9, option = "D") +
  scale_x_continuous(breaks = NULL) +
  facet_wrap(~year, scales = "free") +
  labs(x = "", 
       y = "",
       title = "TF-IDF of My Live Journal Posts",
       subtitle = "Years 2003-2010")
```
Look at the 2009 - clearly my only enteries were my Norse myth college class. 



We can look at the differences between TF-IDF and a regular word count, while accounting for stop words.

```{r}
wordcount <- lj_words_corrected %>%
  count(year, word) %>%
  anti_join(stop_words, by = "word") %>%
  group_by(year) %>%
  top_n(n = 10, wt = n) %>%
  ungroup() %>%
  filter(n >= 3) 
```

```{r echo = FALSE}
wordcount %>%
  ggplot(aes(x = n, y = reorder_within(word, by = n, within = year), 
             fill = factor(year)) ) +
  geom_col() +
  scale_y_reordered() +
  guides(fill = FALSE) +
  viridis::scale_fill_viridis(discrete = TRUE, end = 0.9, option = "D") +
  scale_x_continuous(breaks = NULL) +
  facet_wrap(~year, scales = "free") +
  labs(x = "", 
       y = "",
       title = "Wordcount of My Live Journal Posts",
       subtitle = "Years 2003-2010")
```

### Sentiment

Next I look at sentiment. I remember using live jounral to be super _angsty_. I assumed that I would largely see negative sentiment and words across the years.

```{r}
df_plot <- lj_words_corrected %>%
  left_join (get_sentiments("bing"), by = "word" ) %>%
  rename(bing_sentiment = sentiment) %>%
  left_join (get_sentiments("nrc"), by = "word" ) %>%
  rename(nrc_sentiment = sentiment) %>%
  pivot_longer(cols = c(bing_sentiment, nrc_sentiment), 
               names_to = "sentiment_type", values_to = "sentiment") %>%
  count(sentiment_type, year, sentiment) %>%
  filter(! is.na(sentiment) ) %>%
  rename(count = n ) %>%
  group_by(sentiment_type, year) %>%
  mutate(total = sum(count)) %>%
  ungroup() %>%
  mutate(percent = count / total,
         year_month = ymd(str_c(year, "01", "01", sep = "-"))
         ) 
```

Instead, it seems my words were larely more positive then negative. (Outside of 2009 - where you can see my anxiety attack in the data.) Not as ansgty as I remember!

```{r echo = FALSE}
df_plot %>%
  ggplot(aes(x = year_month, y = percent, 
             color = sentiment)) +
  geom_line() +
  geom_point() +
  geom_text_repel(
    data = filter(df_plot, min(year_month) == year_month),
    aes(label = sentiment),
    max.overlaps = 1000000,
    nudge_x      = -1,
    direction    = "y",
    hjust        = 1,
    segment.size = 0.2,
    xlim = c(-Inf, ymd("2002-12-01") )
  ) +
  scale_y_continuous(label = scales::label_percent(accuracy = 1)) +
  scale_x_date(breaks = scales::pretty_breaks(12), 
               expand = expansion(mult = c(0.20, 0.05)),
               ) +
  scale_color_manual(values = c(
                              "#e41a1c", # anger
                              "#377eb8", # anticipation
                              "#4daf4a", # disgust
                              "black", # fear
                              "orange", # joy
                              "#984ea3", # negative 
                              "#377eb8", # positive
                              "#999999", # sadness 
                              "#f781bf", # surprise
                              "4daf4a") # trust
                     ) +
  guides(color = FALSE) +
  labs(x = "", y = "", title = "% of words of positive sentiment") +
  facet_wrap(~sentiment_type, scales = "free_y", nrow = 2) +
  cowplot::theme_cowplot()
```
Ah, but did I mark my "current mood" / how are you feeling" part as postive as my words are?

```{r echo = FALSE}
extra_sentiemnt <- tibble::tribble(
       ~word, ~sentiment,
            "amused",  "positive",
             "blank",  "negative", 
              "busy",  "negative",
     "contemplative",  "negative",
     "indescribable",  "negative",
            "mellow",  "negative",
              "okay",  "positive",
            "pissed",  "negative",
               "off",  "negative",
          "stressed",  "negative",
           "working",  "negative",
           "content",  "positive"
     )
```

```{r echo = FALSE, warning=FALSE}
df_plot <- lj_words_corrected %>%
  left_join (get_sentiments("bing"), by = "word" ) %>%
  separate_rows(current_mood) %>%
  left_join ( bind_rows(get_sentiments("bing"), extra_sentiemnt), by = c("current_mood" = "word")) %>%
  rename(mood_sentiment = sentiment.y) %>%
  filter(! is.na(sentiment.x), ! is.na(mood_sentiment)) %>%
  group_by(year, mood_sentiment) %>%
  summarise(percent = sum(mood_sentiment == sentiment.x, na.rm = TRUE) / n()) %>%
  ungroup()  

df_plot %>%
  ggplot(aes(x = year, y = percent, color = mood_sentiment)) +
  geom_line() +
  geom_point() +
  geom_text_repel(
        data = filter(df_plot, min(year) == year),
        aes(label = mood_sentiment),
        nudge_x      = -.5,
        direction    = "y",
        segment.size = 0) +
  scale_y_continuous(label = scales::percent) +
  scale_x_continuous(breaks = scales::pretty_breaks(7),
               expand = expansion(mult = c(0.20, 0.05)),
               ) +
  guides(color = FALSE) +
  labs(x = "", y = "", title = "Percent of words that match the sentiement of current mood") +
  cowplot::theme_cowplot()
```
## End :)

So there you have it. Was teenage Erin as emo as I thought? Maybe not! Or maybe I wrote all the most emo jounrals in my physical diary. The world will never know (because those diaries have been lost).
  </div>

  <div class="date">
    Written on 
  </div>

  
<div class="comments">
	<div id="disqus_thread"></div>
	<script type="text/javascript">
    
	    var disqus_shortname = 'astroeringrand'; 

	    (function() {
	        var dsq = document.createElement('script'); dsq.type = 'text/javascript'; dsq.async = true;
	        dsq.src = '//' + disqus_shortname + '.disqus.com/embed.js';
	        (document.getElementsByTagName('head')[0] || document.getElementsByTagName('body')[0]).appendChild(dsq);
	    })();

	</script>
	<noscript>Please enable JavaScript to view the <a href="http://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>
</div>

</article>

    </div>

    <div class="wrapper-footer">
      <div class="container">
        <footer class="footer">
          
<a href="mailto:eringrand@gmail.com"><i class="svg-icon email"></i></a>


<a href="https://github.com/eringrand"><i class="svg-icon github"></i></a>
<a href="https://instagram.com/astroeringrand"><i class="svg-icon instagram"></i></a>
<a href="https://www.linkedin.com/in/eringrand"><i class="svg-icon linkedin"></i></a>


<a href="https://www.twitter.com/astroeringrand"><i class="svg-icon twitter"></i></a>

<a href="https://youtube.com/channel/UCAMkBTcL3PAjgnETfWWKkCQ"><i class="svg-icon youtube"></i></a>

        </footer>
      </div>
    </div>

    
	<!-- Google Analytics -->
	<script>
		(function(i,s,o,g,r,a,m){i['GoogleAnalyticsObject']=r;i[r]=i[r]||function(){
		(i[r].q=i[r].q||[]).push(arguments)},i[r].l=1*new Date();a=s.createElement(o),
		m=s.getElementsByTagName(o)[0];a.async=1;a.src=g;m.parentNode.insertBefore(a,m)
		})(window,document,'script','//www.google-analytics.com/analytics.js','ga');
		
		ga('create', 'UA-59780775-1', 'auto');
		ga('send', 'pageview', {
		  'page': '/Rmds/2022-06-28-LJ.Rmd',
		  'title': 'Reviewing my old live journal posts'
		});
	</script>
	<!-- End Google Analytics -->


  </body>
</html>



